Dispersion distance and the matter distribution of the Universe in dispersion space

### 2015-06-04 writeup/dm_space_distortions.tex
edit to discussion.

We have proposed using cosmological FRB sources as standard pings to trace the 3D 
large-scale structure of the Universe using dispersion distance. It can be seen in
Figure~\ref{f:terms} that the signal is dominated by inhomogeneities in the
electron density along the line-of-sight in each sky direction, inducing mis-estimates of radial
distance and thus apparent clustering. These dispersion-space distortions could
be used
to study the distribution of free electrons in the Universe on large-scales.
There have been other proposals to use FRBs in cosmology 
\citep{2014ApJ...780L..33M,2014MNRAS.443L..11D,
2014ApJ...783L..35D,2014PhRvD..89j7303Z,2014ApJ...788..189G}, however these
schemes have either not been three dimensional
or required externally measured redshifts
for the sources.

>>>>

We have proposed using cosmological FRB sources as standard pings to trace the 3D 
large-scale structure of the Universe using dispersion distance. It can be seen in
Figure~\ref{f:terms} that the signal is dominated by inhomogeneities in the
electron density along the different lines-of-sight,
inducing mis-estimates of radial
distance and thus apparent clustering. These dispersion-space distortions could
be used
to study the distribution of free electrons in the Universe on large-scales.
There have been other proposals to use FRBs in cosmology 
\citep{2014ApJ...780L..33M,2014MNRAS.443L..11D,
2014ApJ...783L..35D,2014PhRvD..89j7303Z,2014ApJ...788..189G}, however these
schemes have either not been three dimensional
or required externally measured redshifts
for the sources.
